---
title: "Homework 9"
author: "Tanya Karagiannis"
date: "November 16, 2015"
output: html_document
---

#### 1. Initial GitHub workflow

a. Pat yourselves on the back if you were able to "fork", then "clone" this repo. Maybe massage your brain, too.

b. Re-save this file with your last and first name as well as altering the title of this file.

#### Tips for creating functions

*Use the least possible number of steps. Work line by line, printing out each value as you create the function. Trying to create a function that will solve the whole problem will typically lead to long debugging times because you will not know where you made the mistake.*

#### 2. if-then-else
Create a function `is.a.number()` that takes a single parameter `X` and returns `"Is a number"` if it is a number, `"Is NA"` if it is an `NA` value, and `"I have no clue"` if it is neither a number nor an `NA` value. Use the `is.na()` and `is.numeric()` functions.

```{r}
is.a.number<- function(x) {
  if(is.numeric(x))
    print("Is a number")
  else if(is.na(x))
    print("Is NA")
  else 
    print("I have no clue")
}
  
```

#### 3. primes 
Create a function that when inputting a single prime number between 3 and 100, it will output a `TRUE` or `FALSE` in a `message()`. Insert an error message as if somebody were to insert a number less than 3, greater than 100, or a non-numeric character. (*Please don't insert all of the prime numbers between 3 and 100 into the function...*)

```{r}
is.prime <- function(x) {
  if (x>3 & x<100 & x==2 ){
    message("TRUE")
  } else if (x>3 & x<100 & any(x %% 2:(x-1) == 0)) {
    message("FALSE")
  } else{
    message("error: x must be a number between 3 and 100")
  } 
} 

```


#### 4. ggplot2

a. Using `ggplot2`, create a function that when inputting a single continuous variable, it will print out a histogram. Include arguments to alter the theme, x-variable label, a title, and a `TRUE` or `FALSE` option to create a density plot.

```{r}
library(ggplot2)

myfun<- function(x,geom,theme,xlab,main,density){
  require(ggplot2)
  p<- qplot(x,geom = "histogram",theme=theme,xlab=xlab,main=main)
  if(theme="grey"){
    condition<- p + theme_grey()
  } else if(theme="bw"){
    condition<- p + theme_bw()
  }    
  if (density=="TRUE"){
    d<- condition + geom_density()
    print(d)
    } else if(density == "FALSE"){
      print(condition)
    }
}

```


b. Similarly, create a function that when inputting two continuous variables, it will print a scatterplot. Additionally, in the console, print the mean and variance of the two variables as well as the coefficient value of the specified x-variable.  Include arguments to alter the title and a `TRUE` or `FALSE` option to include a smoothing method of *lm* aka a simple linear model line in/on the scatterplot.

```{r}
myfun1<- function(x,y,main,smooth){
  require(ggplot2)
  p<- qplot(x,y,main=main)
  if(smooth=="TRUE"){
    d<- p + stat_smooth()
    print(d)
  } else if(smooth=="FALSE"){
    print(p)
  }
  print(mean(x))
  print(mean(y))
  print(var(x))
  print(var(y))
}

```


#### 5. Remaining GitHub workflow

a. Now finish off the workflow of submitting your homework by "committing" the changes locally, "pushing" the changes to YOUR online repo, and finally creating a pull request. 

b. Pat yourselves on the back, again.  You deserved it.
